Learning Network Size while Training with ShrinkNets

### 2018-01-28 paper/ICML/paper.tex

% Use the following line for the initial blind version submitted for review:
\usepackage[accepted]{icml2018}

@@

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Learning Neural Network size with shrinkNets}

@@

We can prove the under the condition: $\forall 1 \leq j \leq p, \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent (\cref{gps_equivalence}). However if we relax this constraint then shrinknet becomes non-convex and has no global minimum (\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}). Fortunately, by adding an extra term to the ShrinkNet regularization term we can proove that:

@@

\subsection{Multi-Target Linear and Logistic regressions}

@@

@@

\subsection{Transfer Learning with ShrinkNets}

@@

\appendix
\section{Appendix}
\subsection{Proofs of propositions}
Unless specified, all the proofs consider the Multi-Target linear regression problem
\begin{proposition}
\label{gps_equivalence}
  $\forall (n, p) \in \mathbb{N}_+^2, \bm{y} \in \mathbb{R}^{n}, \bm{x} \in \mathbb{R}^{p} \lambda \in \mathbb{R}$

@@

\end{proof}
\subsection{Experiment details}
\subsubsection{Multi-Target Linear and Logistic regressions}
\subsubsection{Neuron Removal strategies}
\subsubsection{Convergence and Training Dynamics of Neural networks}
\subsubsection{Hyper-optimization of ShrinkNets}
\subsubsection{Transfer Learning with ShrinkNets}
\subsubsection{Performance}

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite

\bibliography{example_paper}
\bibliographystyle{icml2018}

>>>>

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}

@@

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Learning Neural Network size with ShrinkNets}

@@

We can prove the under the condition: $\forall j\in \intint{1, p}, \norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent (\cref{gps_equivalence}). However if we relax this constraint then shrinknet becomes non-convex and has no global minimum (\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}). Fortunately, by adding an extra term to the ShrinkNet regularization term we can proove that:

@@

\subsection{Multi-Target Linear and Multi-Class Logistic regressions}

We will start evaluating ShrinkNets with the simplest problems possible: linear
and logistic regression. As we showed, Group sparsity share similarities with
our method, this is why we will use it as baseline. We decided to focus on
multi-target linear regression because in the single target case, groups in the
Group Sparsity problem would have a size of one ($\bm{A}$ would be a vector in this
case).

The evaluation will be done on two datasets \texttt{scm1d} and \texttt{oes97}
[ref] for linear regressions and we will use \texttt{gina\_prior2} [ref] and
the \textit{Gas Sensor Array Drift Dataset} [ref] (that we shorten in
\texttt{gsadd}) for logistic regressions.

For each dataset we fit with different regularization parameters and measure
the error and sparsity obtained after convergence. In this context we define sparsity as the ratio of columns that have all their weight under $10^{-3}$ in absolute value. Parameters were choosed in
order to obtain the widest sparsity spectrum. Loss is normalized depending on the problem to be in the $[0, 1]$ range. We summarized the results in
\cref{sparsity_accuracy}. From our experiments it is clear that ShrinkNets can fit the data closer than Group Sparsity for the same amount of sparsity. The fact that we are able to reach very low loss demonstrate that even if our objective function is non convex, in practice it works as good or better as convex alternatives. Details about these datasets and the parameters used
are available in \cref{linear_datasets}.

\begin{figure}
\begin{center}
\includegraphics[height=0.97\columnwidth]{regressions}
\vspace*{-5mm}
\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression. From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}

\end{center}
\vspace*{-4mm}
\end{figure}

@@

In our previous experiment, we showed that the ShrinkNet loss was
reasonable in practice, we are now interested in the impact on
early pruning. The two most important questions to answer are:
What are the impact on convergence speed (i.e. the number of iterations) ?
and: What is the difference in loss with and without early pruning ?

@@

@@

\appendix
\section{Appendix}
\subsection{Proofs}
Unless specified, all the proofs consider the Multi-Target linear regression problem
\begin{proposition}
\label{gps_equivalence}
  $\forall (n, p) \in \mathbb{N}_+^2, \bm{y} \in \mathbb{R}^{n}, \bm{x} \in \mathbb{R}^{p} \lambda \in \mathbb{R}$

@@

\end{proof}
\subsection{Experiment details}
\subsubsection{Multi-Target Linear and Logistic regressions}
\label{linear_datasets}
\subsubsection{Neuron Removal strategies}
\subsubsection{Convergence and Training Dynamics of Neural networks}
\subsubsection{Hyper-optimization of ShrinkNets}
\subsubsection{Performance}

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{OpenML2013}

\bibliography{custom}
\bibliographystyle{icml2018}
